### 2025-07-23 paper/sections/other/main_results.qmd
table added

>>>>

### Integrated Gradients

df = Serialization.deserialize(joinpath(mtbl_dir, "ig.jls")) |>
    df -> transform(df, [:mean, :se] => ByRow((m, s) -> LatexCell("$(round(m, digits=2)) \\pm $(round(s, digits=2))")) => :mean) |>
    df -> select(df, Not(:se)) |>
    df -> DataFrames.unstack(df, :objective, :mean) |>
    df -> rename(df, :full => :CT, :vanilla => :BL) |>
    df -> transform(df, :data => ByRow(d  -> CTExperiments.format_header(d)) => :data)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)
